5_data_viz

### 2018-05-23 scripts/5_data_viz.Rmd
Adding tables and figures to paper

  library(tmap)
  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
  fig_path <- file.path(getwd(), 'images')

@@

  tm_shape(studyarea_sf) + 
    tm_borders(col='gray50', lwd=2) +
  tm_shape(ltr_sf) +
    tm_symbols('geo_mrkt', size=.05, 
               palette = sm_col,
               border.alpha=0, alpha=.03, shape=15)

@@

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   revdens <- ggplot(rev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

   # Add together for plotting potential revenues
   prev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue=pot_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         tidyr::unnest() %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   prevdens <- ggplot(prev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

   strtype.map <- ggplot() +
     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     #ggtitle('Short Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

   ltrtype.map <- ggplot() +
     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     #ggtitle('Long Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
#

>>>>

  library(tmap)
  library(magrittr)
  library(dplyr)
  library(ggplot2)
  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
  fig_path <- file.path(getwd(), 'images')

@@

  sm_col <- c(col_df$rgb[3], col_df$rgb[4], col_df$rgb[5], 
              col_df$rgb[6], col_df$rgb[1])

  png(filename = file.path(fig_path, "ltr_loc_map.png"), 
       width = 4, height = 4, units = 'in', res = 300)
  tm_shape(studyarea_sf) + 
    tm_borders(col='gray50', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray90', lwd=.5) +
  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.3, shape=16, legend.col.show=TRUE)
  dev.off()

  png(filename = file.path(fig_path, "str_loc_map.png"), 
       width = 4, height = 4, units = 'in', res = 300)
  tm_shape(studyarea_sf) + 
    tm_borders(col='gray50', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray90', lwd=.5) +
  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.3, shape=16)
  dev.off()

   strtype_bar <- ggplot() +
     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=sm_col, name='Submarket') +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Short Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

   ltrtype_bar <- ggplot() +
     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=sm_col) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Long Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

     png(filename = file.path(fig_path, "loc_bar.png"), 
       width = 8, height = 4, units = 'in', res = 300)

     ggMultiPlots(strtype_bar, ltrtype_bar, cols=2)
     dev.off()

@@

   dens_cols <- c(col_df$rgb[3], col_df$rgb[1], col_df$rgb[2])

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue=lik_revenue) %>%
                         dplyr::mutate(tenure = 'Short Term (Likely)   ',
                                       alpha = .5),
                       str_tdf %>% 
                         dplyr::select(type, gross_revenue=pot_revenue) %>%
                         dplyr::mutate(tenure = 'Short Term (Potential)   ',
                                       alpha = .4),
                       ltr_df %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'Long-Term   ',
                                       alpha = .9))

  png(filename = file.path(fig_path, "rev_dens.png"), 
       width = 5.5, height = 4, units = 'in', res = 300)

   ggplot(rev_df,
          aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=dens_cols) +
    scale_color_manual(values=dens_cols) +
    ggtitle('Short Term Revenue vs Long Term Revenue') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

# The chart below break down the relative frequency of short and long term rental properties across the five submarkets.

   strtype.map <- ggplot() +
     geom_bar(data=str_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
     scale_fill_manual(values=sm_col) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     theme(plot.title = element_text(hjust = 0.5))
#
#   # Make Long term rental map
#
#   ltrtype.map <- ggplot() +
#     geom_bar(data=ltr_df, aes(x=geo.mrkt, fill=geo.mrkt)) +
#     scale_fill_manual(values=sm_col) +
#     facet_wrap(~type) +
#     ylab('# of Properties\n') + xlab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           axis.text.x=element_blank(),
#           axis.ticks.x=element_blank()) +
#     #ggtitle('Long Term Property Type\nBy Submarket')+
#     theme(plot.title = element_text(hjust = 0.5))
#
